A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-15 paper.tex

\section{Masked Authenticated Messaging}
\label{section:MAM}
MAM enables broadcasting encrypted and authenticated data stream, referring as channel, on the Tangle. The publisher publishes messages that are propagated through the network and can be accessed by the subscribers only. With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.

\subsection{The Message Streams}
A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload. To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root. The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem. Furthermore, the structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload. This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point. Fig.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint.

@@

\subsection{The Advantages of Adopting MAM in Subscription-based Data Trading Infrastructure}
\subsubsection{A Scalable Keys and Data Entry Points Management}
The importance of scalable key and data entry points management increases over time. In MAM, with an entry point (i.e., the address of transaction) and the encryption key, one can derive the following addresses of transaction and retrieve data. Assuming the length of data stream is 7, and each record is encrypted with the same key. With MAM, only 1 key and 1 entry point is required while other distributed storage need to reserve 7 entry points for each data record.

\subsubsection{Data Sreams Classification}
The channel and endpoint structures enable users to be able to easily categorized data streams with respect to different types and usages. For instance, a voice assistant can create a channel every day with multiple endpoints for each gadgets to record daily logs. Another example is sensor devices like AirBox\cite{LASS}, collects environmental data, can split the statistics like PM 2.5 and humidity by time period into separate channels, which is useful for data providers to organize records and to pack into different data products. To do the classification in other distributed storage also encounters the aforementioned scalability problem.

\subsubsection{A Traceable Data Stream}
It allows users to track the changes of data. The hash is widely used to generate checksums of entire package of files, users can compare the hash value of files in order to check the integrity. Yet the hash values of each new version are unrelated and it is not straightforward to point out the differences between versions. MAM benefits from the singly linked-list data structure which attaches messages chronologically, users can easily track the footprints of data change logs as well as checking the validity of modifications with the signature.

>>>>

\section{Masked Authenticated Messaging}
\label{section:MAM}
With MAM, the rights of data access are traded instead of a copy of data in the trading platform, which eliminates the need for data consumers to have additional storage.

\subsection{The Message Streams}
A channel/endpoint is a stream of MAM transaction bundles, which consist of signature and the masked message payload. To publish a MAM message to channel, MAM deploys MSS to sign the message payload to channel, where $channel\ ID = root$ i.e., the MSS Merkle root. The Merkle tree is generated with \textbf{seed}, an identifier of its owner in the IOTA protocol, represents the ownership of all things associated with the user in the IOTA ecosystem.

The structure of channel/endpoint implements forward linking, each address of a message can be derived from the previous one that other entities can fetch the next payload. This design also brings the advantage of forward secrecy, where no one has access to the data back from his/her entry point. Figure.~\ref{fig:mam_structure} shows the structure of MAM channel/endpoint. Furthermore, MAM attaches messages chronologically, which preserves the correct order of IoT streaming data. Though combining other distributed storage like IPFS\cite{IPFS} with signature schemes can also preserve the order of each record, the problem surfaced if the order maintained is wrong.

@@
